---
title: "R-Ladies Melbourne Inc 2022-2023 highlights"
author: "Evie Eker, 2022-2023 President"
date: "April 2023"
output:
  html_document:
    includes:
      after_body:
      - header.html
    theme: cosmo
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(renv)
library(magick)
library(png)
library(grid)
#devtools::install_github("hadley/emo")
#devtools::install_github("ropenscilabs/icon")
library(emo)
library(icons)
library(tufte)
download_fontawesome()
```

Firstly, a quick overview of who we are and where we are at!

# R-Ladies Melbourne Inc: a bit about us

R-Ladies Melbourne is one of the chapters of the worldwide R-Ladies community comprising 229 chapters, 93300 members, across 65 countries (as of today, [source](https://www.meetup.com/en-AU/pro/rladies/)) and the first chapter established in Australia in 2016. In March 2020, R-Ladies Melbourne was incorporated as a not-for-profit organization and we are now also known as R-Ladies Melbourne Inc! 

We are proud to have >2283 members in our [local Meetup community](https://www.meetup.com/en-AU/rladies-melbourne) and also a growing online community of [>2070 followers on Twitter](https://twitter.com/rladiesmelb). We are currently the [top 7th R-Ladies chapter](https://benubah.github.io/r-community-explorer/rladies.html) in terms of membership globally. 

# Slowly overcoming the COVID-19 pandemic challenges

In 2020 we had to pivot to a new way of working. In Australia, 2022 started transitioning out of of lock downs and we were able to hold almost all of our events face to face with one exception. We continuously provided online streaming to keep events flexible for our audience.  

# AGM 2022 and handover to new leadership for 2022-2023

We had our virtual annual general meeting in June 2022 and selected the following new leadership members: 

* Evie Eker, [President]()
* Dai Danyang, [Vice-President](https://twitter.com/Daidaidai2014)
* Sehrish Kanwal, [Secretary](https://twitter.com/skanwal)
* Nikki Rubinstein, [Treasurer](https://twitter.com/nikkirubinstein)

```{r, echo=FALSE, fig.cap="AGM 2022",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/agm2022.png")
grid.raster(img)
```

Thank you to our lovely 2022-2023 R-Ladies Melbourne Inc committee members for all their efforts this year! 
```{r, echo=FALSE, fig.cap="R-Ladies Melbourne Inc Committee Members and Organisers in 2022-2023",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/2022committee.png")
grid.raster(img)
```

# Some exciting internal changes

We have been enjoying the benefits of file migration using the Google account. Huge thanks to our Treasurer [Nikki Rubinstein](https://twitter.com/nikkirubinstein) who has not only spent huge amount of time ensuring this migration was successful, she also worked really hard on ACNC documentation and reporting period alignments.Expression of interest forms for potential speakers has proven itself to be a great tool. If you would like to be a presenter or run a workshop, you can use our EOI form [here](https://docs.google.com/forms/d/1Ax_qADzyWx-rsQcX6sHgasCwCehtbawU03VznDAbhmY/viewform?edit_requested=true). Thanks to committee member [Anna Quaglieri](https://twitter.com/annaquagli) for arranging this form! We have also embraced our using eventbrite for our events as well as meetup to manage the face to face and online attendees! Thanks to our Vice President [Dai Danyang](https://twitter.com/Daidaidai2014) for setting up the eventbrite account. Many thanks to our committee members for handling the event operations.
 

We gathered to say farewell to Shazia! She was instrumental in our operations as our president last year. We are super excited for her new adventure in London. 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Thanks for the sweet send-off <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> 💜 will miss all of you so much! <a href="https://t.co/eBsuq1Wir3">https://t.co/eBsuq1Wir3</a></p>&mdash; Shazia Ruybal Pesántez (@DrShaziaRuybal) <a href="https://twitter.com/DrShaziaRuybal/status/1577803339424636928?ref_src=twsrc%5Etfw">October 5, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

I would like to thank our Vice President Daidai who kept on going supporting the operations online from Brisbane where she is pursuing her PhD. 

# Event highlights in 2022-2023

In the next few sections, I will discuss some of the highlights of our meetups in 2022-2023. Check out the links to the tweets, slides and youtube videos where available. 

## **Upskilling in R: Reproducible research, workflows, spatio-temporal analysis and more!**  
We hosted several meet-ups that covered a wide-range of topics in tidy data and constructing plots, spatial data analysis, workflows in R for reproducibility, tools for open and reproducible research and careers in public health. 


### The workflow of tidy data, constructing plots and making data-driven decisions

One of our biggest supporter and data visualisation expert [Professor Di Cook](https://twitter.com/visnut) from Monash University shared her extensive knowledge in constructing plots using tidy data. Professor Di Cook has introduced the tidy data concepts in practice and showcased how to make inferences from plots. You can access the video recording of this event at [Youtube](https://youtu.be/3wPfPdokaXQ).


```{r, echo=FALSE, fig.cap="The workflow of tidy data, constructing plots and making data-driven decisions workshop, September meet-up",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/di_meetup.png")
grid.raster(img)
```

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Another amazing event given by <a href="https://twitter.com/visnut?ref_src=twsrc%5Etfw">@visnut</a>! Di has been such great mentor to <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> and we are very lucky to have her again 💜. Thanks <a href="https://twitter.com/SayaniGupta07?ref_src=twsrc%5Etfw">@SayaniGupta07</a> for taking the pictures for us! <a href="https://t.co/wRy3IDBgeo">pic.twitter.com/wRy3IDBgeo</a></p>&mdash; Daidai (@Daidaidai2014) <a href="https://twitter.com/Daidaidai2014/status/1565286680881688576?ref_src=twsrc%5Etfw">September 1, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Great to have <a href="https://twitter.com/visnut?ref_src=twsrc%5Etfw">@visnut</a> tonight at <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> <br>Di was the very first speaker of <a href="https://twitter.com/hashtag/rladies?src=hash&amp;ref_src=twsrc%5Etfw">#rladies</a> in September 2016, when we founded the chapter! Awesome to have your continuous support Di! <a href="https://t.co/aIiikUwWtg">pic.twitter.com/aIiikUwWtg</a></p>&mdash; Momeneh Foroutan (@S_Foroutan) <a href="https://twitter.com/S_Foroutan/status/1565249764110675968?ref_src=twsrc%5Etfw">September 1, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>



### Switching between space and time: Spatio-temporal analysis with cubble! 
We were excited to have [Sherry Zhang](https://twitter.com/huizezhangsh) as our guest speaker. Her research focuses on exploring multivariate and spatio-temporal data with visual and exploratory data analysis tools. Sherry focused on sf, tibble and cubble packages then showed us how to create glyph maps in R. My personal favorite part was how she summarised sf operations in one slide which was super handy! This was an excellent workshop where complicated spatial topics were introduced and explored. You can find the slides [here](https://sherryzhang-rladiesmelb2022.netlify.app/#/title-slide) and watch the recording on [Youtube](https://www.youtube.com/watch?v=6Ka021fABxk).

```{r, echo=FALSE, fig.cap="Switching between space and time: Spatio-temporal analysis with cubble workshop, September meet-up",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/sep_meetup.png")
grid.raster(img)
```


<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Getting into different geometrical shapes to store spatial data - all available in <a href="https://twitter.com/hashtag/sf?src=hash&amp;ref_src=twsrc%5Etfw">#sf</a>:<br>- POINTS: vector of pairs of coordinates<br>- LINESTRING: matrix of pairs<br>- POLYGON: list of matrix of pairs vectors<br>- MULTIPOLYGON: list of polygons <a href="https://t.co/7AuJluKQBh">pic.twitter.com/7AuJluKQBh</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1574674420899393536?ref_src=twsrc%5Etfw">September 27, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Looking forward to hearing <a href="https://twitter.com/huizezhangsh?ref_src=twsrc%5Etfw">@huizezhangsh</a> at <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> next week <a href="https://t.co/w5qj3BFI7q">https://t.co/w5qj3BFI7q</a></p>&mdash; Dr Di Cook (@visnut) <a href="https://twitter.com/visnut/status/1571781409425195015?ref_src=twsrc%5Etfw">September 19, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## **Events on reproducible research using R and other open source tools**

### How I use workflowr to create reproducible analyses

Reproducibility is bread and butter of high quality research. We were delighted to have Dr Jovana Maksimovic who works in the field of Bioinformatics and Computational Biology for over 14 years. She walked us through her workflow in R which has proven itself useful in accomplishing reproducibility for researchers in her field. You can find one of the latest examples of Jovana's analysis webpages [here](https://t.co/HYlY5jGzHY). She has been making her research accessible to help others!

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Wonderful slides <a href="https://twitter.com/JovMaksimovic?ref_src=twsrc%5Etfw">@JovMaksimovic</a>! I&#39;m beyond honored that <a href="https://twitter.com/hashtag/workflowr?src=hash&amp;ref_src=twsrc%5Etfw">#workflowr</a> has played a role in your reproducibility journey. Thanks for sharing with the <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> community! <a href="https://t.co/k9WXLjDmz6">https://t.co/k9WXLjDmz6</a></p>&mdash; John Blischak (@jdblischak) <a href="https://twitter.com/jdblischak/status/1580978225265922048?ref_src=twsrc%5Etfw">October 14, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### Choose your own adventure: Tools for Open and Reproducible Research

In this wonderful event we had [Cynthia Huang](https://twitter.com/cynthiahqy) as our guest speaker. Her energy and excitement was infectious! She walked us through version control, literate programming, tidy data, code styles, testing, validation and more! She has shared her experiences and mentioned how overwhelming it can be to adopt to the ever-evolving tech landscape! You can find the slides [here](https://cynthiahqy.quarto.pub/misadventures-with-reproducibility-in-r/#/title-slide).

If you are looking for an entry point to have your environment set up for reproducibility, I highly recommend checking these slides out! 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Join me on Weds night in-person or online for my first R-ladies talk! I’ll be sharing my misadventures with reproducibility in <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a>, and how I deal with my ever-growing “I should learn this” pile. (Or just come for the pizza 🍕) <a href="https://t.co/roGSsICacD">https://t.co/roGSsICacD</a></p>&mdash; Cynthia Huang @cynthiahqy@fosstodon.org (@cynthiahqy) <a href="https://twitter.com/cynthiahqy/status/1597119506458910720?ref_src=twsrc%5Etfw">November 28, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

We also brought some holiday gifts!

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">See you all tonight at <a href="https://twitter.com/WEHI_research?ref_src=twsrc%5Etfw">@WEHI_research</a> to learn about <a href="https://twitter.com/hashtag/reproducibility?src=hash&amp;ref_src=twsrc%5Etfw">#reproducibility</a> &amp; get ready for a Christmas 🎁 with a <a href="https://twitter.com/hashtag/hex?src=hash&amp;ref_src=twsrc%5Etfw">#hex</a> stickers bonanza gifted by <a href="https://twitter.com/posit_pbc?ref_src=twsrc%5Etfw">@posit_pbc</a> !! <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://t.co/tZr5JSwtmJ">https://t.co/tZr5JSwtmJ</a> <a href="https://t.co/O4pRl8dCir">pic.twitter.com/O4pRl8dCir</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1597728026027970560?ref_src=twsrc%5Etfw">November 29, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## **Discussing careers in a joint event** 

We often mix-up our meet-ups by collaborating with other related organizations and groups in Melbourne as well as hear from local experts on topics of interest to our community, such as insights on data viz experiences and consulting and working on collaborative projects! 

### Joint event with WBA: : Navigating Public Health Careers

We had a joint event with [Women in Bioinformatics Australia](https://twitter.com/bioinfowomen) to explore career opportunities in Public Health. We are thankful for their help for organising this event.



Our speakers [Steph Main](https://twitter.com/stephanieEmain), [Daniella Hock](https://twitter.com/daniellahock) and [Dr Danielle Ingle](https://twitter.com/DrDanielleIngle) walked us through their inspirational career journeys and answered questions from the community. 

```{r, echo=FALSE, fig.cap="Joint event with WBA: : Navigating Public Health Careers, February meet-up",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/careers.png")
grid.raster(img)
```

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Thanks so much for having me! <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> <a href="https://twitter.com/bioinfowomen?ref_src=twsrc%5Etfw">@bioinfowomen</a>. Thanks to everyone that came down or listened in. <a href="https://twitter.com/DrDanielleIngle?ref_src=twsrc%5Etfw">@DrDanielleIngle</a> <a href="https://twitter.com/daniellahock?ref_src=twsrc%5Etfw">@daniellahock</a> feel very privileged to work in the <a href="https://twitter.com/hashtag/publichealth?src=hash&amp;ref_src=twsrc%5Etfw">#publichealth</a> sector with you. <a href="https://t.co/nrc7OJgEom">https://t.co/nrc7OJgEom</a></p>&mdash; Steph Main (@stephanieEmain) <a href="https://twitter.com/stephanieEmain/status/1628865082368331776?ref_src=twsrc%5Etfw">February 23, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">I love the parable 🥰🥰🥰<br><br>Aspiring <a href="https://twitter.com/hashtag/Epidemiologist?src=hash&amp;ref_src=twsrc%5Etfw">#Epidemiologist</a> <a href="https://t.co/fCV65JegI1">https://t.co/fCV65JegI1</a></p>&mdash; Olofin, Daniel Oluwafemi🇳🇬 (@daniel_olofin) <a href="https://twitter.com/daniel_olofin/status/1628665638523633665?ref_src=twsrc%5Etfw">February 23, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>



<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Thanks so much for having us <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> and a special thanks so our great sponsors at R, <a href="https://twitter.com/CSL?ref_src=twsrc%5Etfw">@CSL</a> and <a href="https://twitter.com/WeAreServian?ref_src=twsrc%5Etfw">@WeAreServian</a> for hosting us! We will see you at the next one! <a href="https://t.co/BJqZ1WYQts">https://t.co/BJqZ1WYQts</a></p>&mdash; Women in Bioinformatics Australia (@bioinfowomen) <a href="https://twitter.com/bioinfowomen/status/1628690564484042752?ref_src=twsrc%5Etfw">February 23, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

Amazing to have a room full of people again!

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">So happy to see again a <a href="https://twitter.com/hashtag/meetup?src=hash&amp;ref_src=twsrc%5Etfw">#meetup</a> room full of people. Definitely the larger <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> event after covid &amp; big success for <a href="https://twitter.com/bioinfowomen?ref_src=twsrc%5Etfw">@bioinfowomen</a> first event!<br>Super grateful to <a href="https://twitter.com/WeAreServian?ref_src=twsrc%5Etfw">@WeAreServian</a> for hosting the event, it means so much for the community! <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/WomenInScience?src=hash&amp;ref_src=twsrc%5Etfw">#WomenInScience</a> <a href="https://twitter.com/hashtag/PublicHealth?src=hash&amp;ref_src=twsrc%5Etfw">#PublicHealth</a> <a href="https://t.co/EwASKeEn8K">pic.twitter.com/EwASKeEn8K</a></p>&mdash; Anna Quaglieri (@annaquagli) <a href="https://twitter.com/annaquagli/status/1628696902714933255?ref_src=twsrc%5Etfw">February 23, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>





# A personal note 💫

Collaborative and supportive diverse members of the R community motivated me to join R-Ladies Melbourne in 2021. #rstats has been one of the most inclusive communities I wanted to be part of. I'm inspired by women and gender minorities who create amazing R content worldwide and proud to be part of the R-Ladies Melbourne team which is dedicated to creating a safe space for women and gender minorities. It has been a difficult year where we had movements in the committee and more responsibilities fell on to our committee members. We have persevered through the challenges and made it work. I am thankful for our committee who has put together amazing events. Excited to see what the new year will bring! 


# A note from the treasurer 

I joined the RLadies Melbourne organising committee in 2017 and have thoroughly enjoyed working with and learning from the amazing women on the committee. Through seminars, workshops, networking events, incorporation, lockdowns - it's been an amazing ride. I will be stepping down from the committee after this AGM, but will definitely continue to be a part of the RLadies community! I love being part of such an inviting and inclusive group. A huge thank you to the other committee members for their tireless efforts and for being wonderful people to work with 💜

-- Nikki Rubinstein

# Sponsors
Undoubtedly, without our faithful sponsors, we would not be able to be where we are today. A great thanks to all of them for their support over years!
```{r, echo=FALSE, fig.cap="Our amazing sponsors and the stunning view from the venue provided by Nous",echo=FALSE, fig.align="center", out.width = '60%', fig.asp = 0.7}
img <- readPNG("./img/RLadies_Sponsors.png")
grid.raster(img)
```

# Testimonial

We are happy to have always received positive feedback from our speakers, community and long-time supporters. 

> _"R Ladies Melbourne is a globally connected, and consistently insightful meetup group. The organisational team is annually refreshed and coordinates a wonderful list of speakers. It has sustained the community through the isolation members faced during the lockdowns of the past year, with coding and data analysis seminars and workshops. As we transition back to a more normal life, face-to-face meetups have started this past month, giving members a chance to hang out and chat more informally with speakers, over pizza and beer. But it is hybrid, so that members with more personal constraints can join by zoom still. I thoroughly enjoy being a part of this inclusive group."_
>
> `r tufte::quote_footer('-- Di Cook')`

# Find us 

Finally, do not forget to follow the R-Ladies Melbourne Inc if you would like to be updated about us and our events; we do our best to record our events, and make all of our events' materials available on Github.

* `r icons::fontawesome("globe")` [Website](https://rladiesmelbourne-inc.netlify.app)
* `r icons::fontawesome("meetup")` [Meetup](https://www.meetup.com/R-Ladies-Melbourne/)
* `r icons::fontawesome("twitter")` [Twitter](https://twitter.com/RLadiesMelb)
* `r icons::fontawesome("facebook")` [Facebook](https://www.facebook.com/RladiesMelbourne/)
* `r icons::fontawesome("github")` [GitHub](https://github.com/R-LadiesMelbourne)
* `r icons::fontawesome("linkedin")` [LinkedIn](https://www.linkedin.com/company/14675970/admin/)
* `r icons::fontawesome("youtube")` [YouTube](https://www.youtube.com/channel/UClC5yNEjMoE3MmbK-mrV8Ow/videos)

# Acknowledgements
I would like to thank all the past and present committee members for their support and friendship. 
