---
title: "R-Ladies Melbourne Inc 2021-2022 highlights"
author: "Shazia Ruybal-Pesántez, 2021-2022 President"
date: "June 2022"
output:
  html_document:
    includes:
      after_body:
      - header.html
      - footer.html
    theme: cosmo
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magick)
library(png)
library(grid)
# devtools::install_github("hadley/emo")
# devtools::install_github("ropenscilabs/icon")
library(emo)
# library(icons)
library(tufte)
```

Firstly, a quick overview of who we are and where we are at!

# R-Ladies Melbourne Inc: a bit about us

R-Ladies Melbourne is one of the chapters of the worldwide R-Ladies community comprising 216 chapters, 100267 members, across 61 countries (as of today, [source](https://benubah.github.io/r-community-explorer/rladies.html)) and the first chapter established in Australia in 2016. In March 2020, R-Ladies Melbourne was incorporated as a not-for-profit organization and we are now also known as R-Ladies Melbourne Inc! 

We are proud to have >2160 members in our [local Meetup community](https://www.meetup.com/en-AU/rladies-melbourne) and also a growing online community of [>1970 followers on Twitter](https://twitter.com/rladiesmelb). We are currently the [top 7th R-Ladies chapter](https://benubah.github.io/r-community-explorer/rladies.html) in terms of membership globally. 

# Continued COVID-19 pandemic challenges
In 2020 we had to pivot to a new way of working. In Australia, 2021 was still a year of lock downs and uncertainty with respect to COVID-19 restrictions. Thus the majority of our events in 2021-2022 were held online, with a return to an our first in-person event in May 2022. 

# AGM 2021 and handover to new leadership for 2021-2022

We had our virtual annual general meeting in May 2021 and selected the following new leadership members: 

* Shazia Ruybal-Pesántez, [President](https://twitter.com/DrShaziaRuybal)
* Yuri Song, [Vice-President]()
* Sehrish Kanwal, [Secretary](https://twitter.com/skanwal)
* Nikki Rubinstein, [Treasurer](https://twitter.com/nikkirubinstein)

```{r, echo=FALSE, fig.cap="AGM 2021",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/agm2021.png")
grid.raster(img)
```

We also have several other committee members outside of the core NFP leadership team that hold key roles such as managing our social media pages and GitHub. Thank you to our lovely 2021-2022 R-Ladies Melbourne Inc committee members for all their efforts this year! 
```{r, echo=FALSE, fig.cap="R-Ladies Melbourne Inc Committee Members and Organisers in 2021-2022",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/2021committee.png")
grid.raster(img)
```

# Advisory board changes

In addition to formal and internal roles that have been previously described in detail [here](https://momenehforoutan.github.io/RLadiesMelbInc_2019/), the previous committee introduced the notion of "advisory board" members in 2020, as described [here](https://skanwal.github.io/RLadiesMelbInc_2020/). One of our advisory board members [Göknur Giner](https://twitter.com/goknurginer) stepped down from her role, and we also welcomed a previous leadership team member [Marie Trussart](https://twitter.com/mtrussart) to our advisory board. 

# Some exciting internal changes

We have created a Google Workspace account for R-Ladies Melbourne Inc and purchased a domain name for our website. Huge thanks to our Treasurer [Nikki Rubinstein](https://twitter.com/nikkirubinstein) who has been instrumental in migrating our important files into our new shared space. We have also streamlined many of our internal processes, including automatically-generated financial reporting, easy-to-use reimbursement forms and expression of interest forms for potential speakers. We have also created some new roles for our community - we now accept expressions of interest for those who would like to join our committee (open to those that identify as a women or other underrepresented genders), as well as those who would like to join our Events Task Force (open to all). Thanks to committee member [Anna Quaglieri](https://twitter.com/annaquagli) for this suggestion! We have also embraced our online presence/virtual events and begun to make better use of polling options through Twitter and Zoom to get to know our community better and what they would like to see from us! Thanks to committee members [Caitlin Bourke](https://twitter.com/bourke_cait) and [Evie Giz]() for running many of these.

# Our brand new website 😍! 
Check it out [here](https://rladiesmelbourne-inc.netlify.app)! We have also re-branded slightly with our beautiful koala logo, which was created by [Roberto Bonelli](https://twitter.com/robbie_bonelli).

```{r, echo=FALSE, fig.cap="New R-Ladies Melbourne Inc website",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/website.png")
grid.raster(img)
```

# Event highlights in 2021-2022

In the next few sections, I will discuss some of the highlights of our meetups in 2020-2021. Don't forget to check out our live-tweets and threads from each of our events for more details (inserted into this report as quotes). 

## **Upskilling in R: new R packages, stats, software design and more!**  
We hosted several meet-ups that covered a wide-range of topics in newly developed R packages, design-thinking principles and building new things in R such as your CV or a new geom. 

### A remote glimpse into the useR! 2021 conference

Our committee member [Anna Quaglieri](https://twitter.com/annaquagli), Bioinformatics Data Scientist at [Mass Dynamics](https://www.massdynamics.com), gave us a recap of the [virtual useR! 2021 conference](https://user2021.r-project.org) and kicked off our events as the new 2021-2022 committee! Anna told us about some exciting new developments that were presented at useR!, you can access her slides at [user2021-rladies-melbourne.netlify.app/#1](https://user2021-rladies-melbourne.netlify.app/#1).

```{r, echo=FALSE, fig.cap="A Remote Glimpse into the useR! 2021 conference, August meet-up",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./img/aug_meetup.png")
grid.raster(img)
```

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Here are the topics that <a href="https://twitter.com/annaquagli?ref_src=twsrc%5Etfw">@annaquagli</a> will be presenting today about the <a href="https://twitter.com/hashtag/userR2021?src=hash&amp;ref_src=twsrc%5Etfw">#userR2021</a> conference: <a href="https://t.co/8xPVWORB1L">pic.twitter.com/8xPVWORB1L</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1422464617280770049?ref_src=twsrc%5Etfw">August 3, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### Anomalies, you can't escape them! 
We had the pleasure of hearing from applied mathematician, [Sevvandi Kandanaarachchi](https://twitter.com/Sevvandik) from RMIT Mathematics about her new package [{outlierensembles}](https://sevvandi.github.io/outlierensembles/). 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to our event presented by <a href="https://twitter.com/Sevvandik?ref_src=twsrc%5Etfw">@Sevvandik</a> : Anomalies, you can&#39;t escape them: <a href="https://t.co/aPJky9hWUs">pic.twitter.com/aPJky9hWUs</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1438407330706583553?ref_src=twsrc%5Etfw">September 16, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### The Art of Design: Software & Experimental Design 
Our long-time supporter and community member, [Emi Tanaka](https://twitter.com/statsgen), who is a lecturer in statistics at Monash University gave a talk about the art of design for both software and experimental designs. Her slides can be found at [github.com/emitanaka/slides-RLadiesMelb2021](https://github.com/emitanaka/slides-RLadiesMelb2021).

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Catch up with the event with our live tweets! Presented by <a href="https://twitter.com/statsgen?ref_src=twsrc%5Etfw">@statsgen</a> <a href="https://t.co/zvD8kxACg1">pic.twitter.com/zvD8kxACg1</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1452894922751680513?ref_src=twsrc%5Etfw">October 26, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### Automate your CV using RMarkdown: easy as 1, 2, knit! 
We tried out a lunch-time meet-up since I was overseas at the time of my talk and it attracted a lot of people in different time zones! If you've ever wondered how to create your CV in R, you can follow along at [shaziaruybal.github.io/automate-cv-rmd/#1](https://shaziaruybal.github.io/automate-cv-rmd/#1).

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to our first event of 2022! <a href="https://twitter.com/DrShaziaRuybal?ref_src=twsrc%5Etfw">@DrShaziaRuybal</a> will walk us through how to knit your CV using <a href="https://twitter.com/hashtag/rmarkdown?src=hash&amp;ref_src=twsrc%5Etfw">#rmarkdown</a>! Tune in to our live tweets if you are unable to join. We will make the recording available on our youtube!</p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1489406787547955205?ref_src=twsrc%5Etfw">February 4, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### Building a new geom in ggplot2
Our latest event took our R up-skilling up a notch with [Sayani Gupta](https://twitter.com/sayanigupta07), a statistician from Monash University showing us how to create a new geom in `{ggplot2}`! She talked us through her new R package [{gghdr}](https://sayani07.github.io/gghdr/), you can follow along with her slides at [sayanigupta-rladies22.netlify.app/#1](https://sayanigupta-rladies22.netlify.app/#1).

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to the live tweets from R-Ladies Melbourne May event. We have Dr. <a href="https://twitter.com/SayaniGupta07?ref_src=twsrc%5Etfw">@SayaniGupta07</a> presenting us how to create a geom in ggplot2 package. <a href="https://t.co/2hVlwTeOHq">pic.twitter.com/2hVlwTeOHq</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1529014297137127426?ref_src=twsrc%5Etfw">May 24, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## **Workshops and joint events: artificial intelligence, data viz, consulting, and more!** 
We often mix-up our meet-ups by collaborating with other related organizations and groups in Melbourne as well as hear from local experts on topics of interest to our community, such as insights on data viz experiences and consulting and working on collaborative projects! 

### Joint event with WiMLDS: AI Ethics Workshop
In conjunction with our friends at [Women in Machine Learning and Data Science](https://www.meetup.com/Melbourne-Women-in-Machine-Learning-and-Data-Science/) we co-hosted a meet-up on artificial intelligence ethics, led by [Laura Summers](https://twitter.com/summerscope), the founder of debias.ai, the human behind Ethics Litmus Tests, fairXiv, and the Melbourne Fair ML reading group.

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to our AI ethics workshop with <a href="https://twitter.com/summerscope?ref_src=twsrc%5Etfw">@summerscope</a> - a joint event with <a href="https://twitter.com/WiMLDS_Melb?ref_src=twsrc%5Etfw">@WiMLDS_Melb</a>! <a href="https://t.co/OCJe1xP8QS">pic.twitter.com/OCJe1xP8QS</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1498186234937499660?ref_src=twsrc%5Etfw">February 28, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

### Data viz for mass audiences
Many of us in Australia followed the COVID-19 pandemic data by following websites such as [covid19data.com.au](https://covid19data.com.au). We were extremely excited to hear from the creator of [covid19data.com.au](https://covid19data.com.au), [Juliette O'Brien](https://twitter.com/juliette_io) on her experience as a digital and data journalist launching and managing the tracking website during such a dynamic time! 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to our April event Data viz for mass audiences with <a href="https://twitter.com/juliette_io?ref_src=twsrc%5Etfw">@juliette_io</a> live tweets!<a href="https://twitter.com/hashtag/rladies?src=hash&amp;ref_src=twsrc%5Etfw">#rladies</a> <a href="https://twitter.com/hashtag/rladiesmelbourne?src=hash&amp;ref_src=twsrc%5Etfw">#rladiesmelbourne</a> <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/data?src=hash&amp;ref_src=twsrc%5Etfw">#data</a> <a href="https://twitter.com/hashtag/Datavisualization?src=hash&amp;ref_src=twsrc%5Etfw">#Datavisualization</a> <a href="https://t.co/GvXqbULfje">pic.twitter.com/GvXqbULfje</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1511973420174508033?ref_src=twsrc%5Etfw">April 7, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


### How to do analysis for others without going crazy: my mistakes in consulting!
Since many of us work on collaborative projects and many members of our community also work in consulting, we invited [Taya Collyer](https://twitter.com/TayaCollyer), a biostatistician and public health researcher to tell us about her mistakes (and advice!) in consulting. 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Welcome to our March event live tweets! <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/rladies?src=hash&amp;ref_src=twsrc%5Etfw">#rladies</a> <a href="https://twitter.com/hashtag/rladiesmelbourne?src=hash&amp;ref_src=twsrc%5Etfw">#rladiesmelbourne</a> <a href="https://t.co/lD0HoyzsYN">pic.twitter.com/lD0HoyzsYN</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1500723360824958978?ref_src=twsrc%5Etfw">March 7, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


## **Community outreach**
Part of our mission is to inspire women and those who identify as women or underrepresented genders to feel part of a safe, inclusive and welcoming community! When we get the opportunity we are always open to support community outreach, particularly to inspire girls in STEM to get into coding! 

### It Takes a Spark! Conference
Since 2019 we have hosted a workshop on "How to Become a Disease Detective" using R and epidemiology at the [It Takes a Spark! conference](https://spark-educonferences.com.au/it-takes-a-spark-2022-melbourne/), which is aimed at inspiring girls to get into STEM. 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">We were delighted to present a workshop at the “It Takes a Spark!” 2022 Conference✨<a href="https://twitter.com/DrShaziaRuybal?ref_src=twsrc%5Etfw">@DrShaziaRuybal</a> &amp; <a href="https://twitter.com/bourkecait?ref_src=twsrc%5Etfw">@bourkecait</a> showed Year 8-10 <a href="https://twitter.com/hashtag/STEM?src=hash&amp;ref_src=twsrc%5Etfw">#STEM</a> students how to become “Disease Detectives” and solve a mysterious disease outbreak using <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> and <a href="https://twitter.com/hashtag/epidemiology?src=hash&amp;ref_src=twsrc%5Etfw">#epidemiology</a> 👩‍💻 <a href="https://twitter.com/hashtag/ItTakesASpark?src=hash&amp;ref_src=twsrc%5Etfw">#ItTakesASpark</a> <a href="https://t.co/XkwYqkRoyj">pic.twitter.com/XkwYqkRoyj</a></p>&mdash; R-Ladies Melbourne Inc (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1522391527955525633?ref_src=twsrc%5Etfw">May 6, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

Some reflections from [Caitlin Bourke](https://twitter.com/bourke_cait) about the conference and her experience are below. 

> _"Attending the it takes a spark conference in may this year was one of the highlights of my time on the committee this year. Shazia and I attended the conference with around 400 (maybe fact-check) high school students from across Victoria. We facilitated a workshop for 35 Years 8-10, introducing topics of epidemiology and using some basic r data wrangling and plotting functions to solve an outbreak of food poisoning. It was really quite inspiring how quickly the students took to learning the concepts and basic functionality of R and can only bode well for the future of stem and data science"_
>
> `r tufte::quote_footer('-- Caitlin Bourke, R-Ladies Melbourne Inc Committee Member')`


# My personal remarks 💜
R-Ladies Melbourne has been such an amazing community to be part of. I joined the committee in 2019 because I loved the mission of R-Ladies global and R-Ladies Melbourne and wanted to be part of the "movement"! Through R-Ladies Melbourne Inc I have met great friends and have been fortunate to count on the support of many amazing R-ladies when I was nominated as president last year. Our previous president, Sehrish spoke in great detail of how the COVID-19 pandemic affected us in 2020-2021 during her [annual report remarks](https://skanwal.github.io/RLadiesMelbInc_2020/), and my tenure as president was similar. It was a tough time for most of us on both a personal and professional level, and given R-Ladies Melbourne Inc is completely volunteer-led, I was fortunate to count on a fabulous committee that kept us going and worked together to still host meaningful virtual meet-ups for our community. I don't think I only speak for myself when I say that R-Ladies Melbourne Inc is a fabulous and supportive community - the committee members were extremely flexible and supportive of my personal circumstances when I had to travel for almost 5 months to my home country of Ecuador! Despite the challenges, we had a very successful year in terms of being able to deliver fantastic and interesting meet-up topics but also in improving many of our internal processes, which will hopefully make many things more streamlined for future leadership teams to come. On a very personal note, I am extremely sad to be stepping down not only of the President role that I feel very fortunate to have held this year, but also leaving the R-Ladies Melbourne wider community as I am taking up a new position in London. I hope R-Ladies London will have a spot for me! 💜

# Sponsors
Undoubtedly, without our faithful sponsors, we would not be able to be where we are today. A great thanks to all of them for their support over years!
```{r, echo=FALSE, fig.cap="Our amazing sponsors and the stunning view from the venue provided by Nous",echo=FALSE, fig.align="center", out.width = '60%', fig.asp = 0.7}
img <- readPNG("./img/RLadies_Sponsors.png")
grid.raster(img)
```

# Testimonial

We are happy to have always received positive feedback from our speakers, community and long-time supporters. 

> _"R Ladies Melbourne is a globally connected, and consistently insightful meetup group. The organisational team is annually refreshed and coordinates a wonderful list of speakers. It has sustained the community through the isolation members faced during the lockdowns of the past year, with coding and data analysis seminars and workshops. As we transition back to a more normal life, face-to-face meetups have started this past month, giving members a chance to hang out and chat more informally with speakers, over pizza and beer. But it is hybrid, so that members with more personal constraints can join by zoom still. I thoroughly enjoy being a part of this inclusive group."_
>
> `r tufte::quote_footer('-- Di Cook')`

# Find us 

Finally, do not forget to follow the R-Ladies Melbourne Inc if you would like to be updated about us and our events; we do our best to record our events, and make all of our events' materials available on Github.

* [Website](https://rladiesmelbourne-inc.netlify.app)
* [Meetup](https://www.meetup.com/R-Ladies-Melbourne/)
* [Twitter](https://twitter.com/RLadiesMelb)
* [Facebook](https://www.facebook.com/RladiesMelbourne/)
* [GitHub](https://github.com/R-LadiesMelbourne)
* [LinkedIn](https://www.linkedin.com/company/14675970/admin/)
* [YouTube](https://www.youtube.com/channel/UClC5yNEjMoE3MmbK-mrV8Ow/videos)

# Acknowledgements
I would like to thank all the past and present committee members for their support and friendship. 